---
title: "Worker Master Data"
author: "Jooree Ahn"
date: "December 13, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Load packages
library(RODBC)
library(foreign)
library(stringr)
library(tidyr)
library(dplyr)

# Load data from database
con <- odbcConnect("POC") # db connection

full_dat <- sqlQuery(con, "select * from poc_survey.master_worker_data_p1")
```

# Transform Data
The following process transforms the data as such:

1. Extracts a unit number from `SSPS_ID`
2. Creates a unique `unit id` by uniting the unit number with the office number
3. Recodes program areas such that 'Yes' = 1 and 'No' or NA = 0
4. Creates a count of program areas selected per worker
5. Flags workers that have only DLR CPS, DLR Licensing, Intake, or Adoption selected as their program area

```{r}
transformed_dat <- full_dat %>%
  # Extract unit number from SSPS_ID
  separate(SSPS_ID, c("unit", "ssps_end"), sep = 2) %>%
  # Create unit id by uniting  unit number with office number
  unite(unit_id, c("unit", "office_number"), sep = "", remove = FALSE) %>%
  # Recode program areas where 'No = 2' or is NA to 0
  mutate(q1a = ifelse(q1a == 2 | is.na(q1a), 0, q1a),
         q1b = ifelse(q1b == 2 | is.na(q1b), 0, q1b),
         q1c = ifelse(q1c == 2 | is.na(q1c), 0, q1c),
         q1d = ifelse(q1d == 2 | is.na(q1d), 0, q1d),
         q1e = ifelse(q1e == 2 | is.na(q1e), 0, q1e),
         q1f = ifelse(q1f == 2 | is.na(q1f), 0, q1f),
         q1g = ifelse(q1g == 2 | is.na(q1g), 0, q1g),
         q1h = ifelse(q1h == 2 | is.na(q1h), 0, q1h)) %>%
  # Create count of program areas per worker
  mutate(prg_area_sum = rowSums(dplyr::select(., q1a:q1h), na.rm = TRUE)) %>%
  # Flag where worker only has one of the 'Other' roles
  mutate(only_dlr_cps = ifelse(q1a == 0 & q1b == 0 & q1c == 0 & q1d == 0 & q1e == 1, 1, 0),
         only_dlr_lic = ifelse(q1a == 0 & q1b == 0 & q1c == 0 & q1d == 0 & q1f == 1, 1, 0),
         only_intake = ifelse(q1a == 0 & q1b == 0 & q1c == 0 & q1d == 0 & q1g == 1, 1, 0),
         only_adoption = ifelse(q1a == 0 & q1b == 0 & q1c == 0 & q1d == 0 & q1h == 1, 1, 0),
         only_other = ifelse(only_dlr_cps == 1 | only_dlr_lic == 1 | only_intake == 1 | only_adoption == 1, 1, 0))
```

# Filter Data
The following process filters out workers who:

1. Do not have a unit number or an office number
2. Do not have any program areas selected
3. Only have DLR CPS, DLR Licensing, Intake, or Adoption selected as their program area
4. Are in a unit id with less than two people

```{r}
subset_dat <- transformed_dat %>%
  # Drop where unit number or office number is missing
  filter(!is.na(unit),
         !is.na(office_number),
         # Drop where no program area is indicated
         prg_area_sum > 0,
         # Drop where worker only does one of the 'Other' roles
         only_other == 0) %>%
  # Create count of people for each unit id (this must be done after all other filters)
  group_by(unit_id) %>%
  mutate(unit_id_count = n()) %>%
  ungroup() %>%
  # Drop where unit has less than two people
  filter(unit_id_count > 1)
```

# Save Data
```{r}
write.csv(subset_dat, "S:/Practice Model/Project_Data/worker_master_dat.csv")
write.foreign(subset_dat, "S:/Practice Model/Project_Data/worker_dat.txt", "S:/Practice Model/Project_Data/worker_master_dat.sps",   package = "SPSS")
```

